---
title: "Vignette of Lab7 package"
author: "Thi and Somaya"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package consists of `ridgereg` function which performs ridge regression. The function takes a formula object, dataset and pamameter lamda and return a ridgered object. 

## How to install and load

### Install 

To install the package [devtools] in [RStudio](https://www.rstudio.com/), you can just run the following command
```{r, eval = FALSE}
install.packages("devtools")
```


After the installation of `devtools`, we can simply run the following command in the RStudio console
```{r, eval = FALSE}
devtools::install_github(repo = "thiph169/ARP-lab-7/", 
                         build_vignette = TRUE)
```

### Load

After the installation is successful,load the package using

```{r}
library(lab7)
data(iris)
```

## Usage

The `ridgereg` functions contains the methods `print`, `predict`, and `coef`. Below are examples using `iris` data set


### print()  

this method prints out the coefficients and coefficient names, similar as done by the `lm` class.
Example:   

```{r, echo=FALSE}
lab7:::ridgereg$new(Petal.Length~Species, data=iris, lamda=0)$print()

```

### predict()  

This method returns the predicted values y^, it should be able to predict for new dataset similar to the `predict()` function for the `lm()` package.  

Example:   

```{r, echo=FALSE}
lab7:::ridgereg$new(Petal.Length~Species, data=iris, lamda=0)$predict()
```

### coef()  

This method returns the ridge regression coefficients.   

Example:    

```{r, echo=FALSE}
lab7:::ridgereg$new(Petal.Length~Species, data=iris, lamda=0)$coef()
```


